Binary companions of red clump stars

### 2017-08-04 paper/main.tex
content

% adjust ASS-TEX shit
\setlength{\parindent}{1.\baselineskip}

@@

@@

APW: Should we start this section with a set of named assumptions, as we
did in Anderson et al?

Summary of \thejoker\ and what it does.

@@

@@

>>>>

% adjust AAS-TEX shit
\setlength{\parindent}{1.\baselineskip}

@@

APW: Opening sentence: If we see RV changes, there must be binaries!
Can we infer binary populations from bad data?

@@

Our approach here is to proceed in two phases.
In the first phase, we obtain a posterior sampling in binary-system
parameter space for every individual star, treating it as a
single-lined (SB1) spectroscopic binary system with a single
companion.
This sampling is performed under a relatively uninformative prior pdf,
which will be called the ``\emph{interim prior}''.
These samplings are used to discover and characterize individual binary-star
systems, and generate (among other things) a catalog of binaries.
In the second phase, we perform a hierarchical inference of the binary
population, using (responsibly) these samplings under the interim
prior as inputs.
In the second phase we use all samplings of all stars, not just those that
pass our thresholds for discovery as binary systems.
In this \sectionname, we describe the first phase, that is, the
individual-system sampling phase for discovery and characterization.

We make our posterior samplings under the following assumptions:
\begin{description}
\item[foo] whatevs
\item[bar] and more
\end{description}

Summary of \thejoker\ and what it does; that is, that it obeys the
relevant parts of our assumptions.

@@

Examples of outputs and etc.

@@

Thresholding on what now?

Catalog.

Some highlights from this catalog.
